### 2023-10-24 generalExploration.Rmd
minor rename

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                print("hmmmaybe")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }
            #if(runif(1)<d)population[[ind]]=NULL
        }

>>>>

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                print("marriage attempt")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }
            #if(runif(1)<d)population[[ind]]=NULL
        }
